Notes

### 2021-08-15 articles/notes/notes.tex
paper notes and article notes

% Created 2021-07-13 Tue 22:21
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{natbib}
\setlist{noitemsep}
\author{Benjamin Goldman}
\date{\today}
\title{Notes}
\hypersetup{
 pdfauthor={Benjamin Goldman},
 pdftitle={Notes},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.5)}, 
 pdflang={English}}
\begin{document}

@@

\section{\cite{an2017feedback}}
\label{sec:org3655487}

@@

\section{\cite{bjerknes1969atmospheric}}
\label{sec:org136b470}

@@

\section{{\bfseries\sffamily TODO} \cite{boer2000transient}}
\label{sec:org04662d3}

\section{\cite{cai2018increased}}
\label{sec:org328012a}

@@

\section{{\bfseries\sffamily TODO} \cite{chen2015causes}}
\label{sec:orgd3d49d0}

\section{\cite{chen2017possible}}
\label{sec:org21b124c}

@@

\section{{\bfseries\sffamily TODO} \cite{deser2020isolating}}
\label{sec:org43ffddf}

@@

\section{{\bfseries\sffamily TODO} \cite{dewitte2012reinterpreting}}
\label{sec:org2367605}

\section{\cite{emile2007nino}}
\label{sec:orgbb125ce}

@@

\section{\cite{graham2014effectiveness}}
\label{sec:org7d28ecd}

@@

\section{\cite{hu2018cross}}
\label{sec:org9e81eeb}
\section{\cite{jia2019weakening}}
\label{sec:orgc220f64}
\section{{\bfseries\sffamily TODO} \cite{jimenez2016record}}
\label{sec:org422a8cd}
\section{\cite{kay2015community}}
\label{sec:org5b0d352}
\section{\cite{kestin1998time}}
\label{sec:orgffee63b}
\section{{\bfseries\sffamily TODO} \cite{kim2014response}}
\label{sec:org1250259}
\section{{\bfseries\sffamily TODO} \cite{kohyama2018weakening}}
\label{sec:orgf9af32a}
\section{\cite{levine2017impact}}
\label{sec:org4982a37}
\section{\cite{lorenz1963deterministic}}
\label{sec:org5b50a4f}
\section{{\bfseries\sffamily TODO} \cite{liu2007atmospheric}}
\label{sec:org4049c31}
\section{\cite{lubbecke2014assessing}}
\label{sec:org7b0850f}
\section{\cite{maher2018enso}}
\label{sec:orgdd094cf}
\section{\cite{nowack2017role}}
\label{sec:org9238fee}
\section{\cite{phillips2014evaluating}}
\label{sec:org830cbdd}
\section{{\bfseries\sffamily TODO} \cite{rashid2016atmospheric}}
\label{sec:orge93d755}
\section{{\bfseries\sffamily TODO} \cite{ropelewski1987global}}
\label{sec:org47cae0c}
\section{{\bfseries\sffamily TODO} \cite{son2010impact}}
\label{sec:orga87c549}
\section{{\bfseries\sffamily TODO} \cite{stevenson2010enso}}
\label{sec:org6de73f7}
\section{{\bfseries\sffamily TODO} \cite{stevenson2012will}}
\label{sec:org697dce3}
\section{\cite{stevenson2012significant}}
\label{sec:orge1990c0}
\section{\cite{stevenson2017forced}}
\label{sec:orgf634322}

\section{\cite{torrence1998practical}}
\label{sec:org2e0f412}

@@

\section{{\bfseries\sffamily TODO} \cite{vecchi2006weakening}}
\label{sec:orgb996a82}
\section{\cite{vega2017analysis}}
\label{sec:orga1fc1a2}
\section{{\bfseries\sffamily TODO} \cite{wang2016nino}}
\label{sec:orge694acd}
\section{{\bfseries\sffamily TODO} \cite{yeo2016role}}
\label{sec:orgeaa77a3}
\section{{\bfseries\sffamily TODO} \cite{zhang2019review}}
\label{sec:org471ee8c}
\section{{\bfseries\sffamily TODO} \cite{zheng2016intermodel}}
\label{sec:org1371712}
\section{\cite{zheng2017response}}
\label{sec:org013bb4e}

\bibliographystyle{apalike}
\bibliography{references}
\end{document}

>>>>

% Created 2021-08-15 Sun 14:58
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{natbib}
\usepackage[margin=1in]{geometry}
\setlist{noitemsep}
\author{Benjamin Goldman}
\date{\today}
\title{Notes}
\hypersetup{
 pdfauthor={Benjamin Goldman},
 pdftitle={Notes},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.5)}, 
 pdflang={English}}
\begin{document}

@@

\section{\cite{an2017feedback}}
\label{sec:org87b42f5}

@@

\section{\cite{bjerknes1969atmospheric}}
\label{sec:org7b6b0b3}

@@

\section{{\bfseries\sffamily TODO} \cite{boer2000transient}}
\label{sec:org8596bf6}

\section{\cite{cai2018increased}}
\label{sec:org6b26555}

@@

\section{{\bfseries\sffamily TODO} \cite{chen2015causes}}
\label{sec:orgc84b0ce}

\section{\cite{chen2017possible}}
\label{sec:org826e065}

@@

\section{{\bfseries\sffamily TODO} \cite{deser2020isolating}}
\label{sec:orgd7f2af0}

@@

\section{{\bfseries\sffamily TODO} \cite{dewitte2012reinterpreting}}
\label{sec:org1549366}

\section{\cite{emile2007nino}}
\label{sec:org5ae4263}

@@

\section{\cite{gistemp2019giss}}
\label{sec:org3883bf1}

\begin{itemize}
\item citation for GISSTEMP dataset
\end{itemize}

\section{\cite{graham2014effectiveness}}
\label{sec:orga71922b}

@@

\section{\cite{hu2018cross}}
\label{sec:org025902a}

\begin{itemize}
\item Observed and model data used
\item Strengthening in cross-equatorial winds changes ITCZ position, weakening ENSO.
\end{itemize}

\section{\cite{jia2019weakening}}
\label{sec:org43889c8}

\begin{itemize}
\item My first paper!
\item Atlantic Niño/Niña is correlated/causes opposite ENSO form
\item Global warming is weakening this connection, impairing prediction efforts
\item CESM5 coupled models used
\item Correlation coefficient
\end{itemize}

\section{{\bfseries\sffamily TODO} \cite{jimenez2016record}}
\label{sec:org518f64c}

\section{{\bfseries\sffamily TODO} \cite{kay2015community}}
\label{sec:orga1c53a6}

\begin{itemize}
\item CESM1 LE citation
\end{itemize}

\section{\cite{kestin1998time}}
\label{sec:org97d4f0c}

\begin{itemize}
\item apply wavelet and Fourier analysis to ENSO in observed data
\item 2-3 year ENSO reduced from 1920-1960
\item Stochastic model used to simulate ENSO agrees with analysis of observed data
\item Concluded that models are reasonably accurate for simulating decadal ENSO variability
\end{itemize}

\section{{\bfseries\sffamily TODO} \cite{kim2014response}}
\label{sec:org4882548}
\section{{\bfseries\sffamily TODO} \cite{kohyama2018weakening}}
\label{sec:orgdf9c6cc}

\section{\cite{levine2017impact}}
\label{sec:orgea9bd4a}

\begin{itemize}
\item Observed ICOADS data
\item Inverse relationship between AMO index and ENSO SPB strength
\item Coupled model simulation
\end{itemize}

\section{\cite{lorenz1963deterministic}}
\label{sec:org9ccfa1a}

\begin{itemize}
\item Nonlinear differential equations have solutions that must be solved numerically
\item When graphed in phase space, these solutions form attractors that never repeat themselves
\item Many natural phenomena, including weather, are chaotic
\item Accurate long-term weather prediction is likely impossible
\end{itemize}

\section{{\bfseries\sffamily TODO} \cite{liu2007atmospheric}}
\label{sec:org771a8c8}

\section{\cite{lubbecke2014assessing}}
\label{sec:orgccacdfc}

\begin{itemize}
\item Change in ENSO characteristics after 2000
\item Lower thermocline slope reduces TH feedback, making it harder for strong ENSO to form
\end{itemize}

\section{\cite{maher2018enso}}
\label{sec:org8070eaf}

\begin{itemize}
\item Use two different large ensembles
\item ENSO has lots of internal variability in models
\item 30-40 members of an ensemble are needed to detect significant changes to ENSO in the ensemble mean
\item Increase in ENSO amplitude in worst case (RCP8.5) scenario
\end{itemize}

\section{\cite{nowack2017role}}
\label{sec:org123f132}

\begin{itemize}
\item Model simulations that are forced with differing levels of greenhouse and aerosol emissions
\item Concluded that aerosol forcing decreases greenhouse strengthening of ENSO
\end{itemize}

\section{{\bfseries\sffamily TODO} \cite{pachauri2014climate}}
\label{sec:orgb3ac32a}

\begin{itemize}
\item IPCC report 2014
\end{itemize}

\section{\cite{phillips2014evaluating}}
\label{sec:orgc0ab115}

\begin{itemize}
\item Citation for CVDP data
\end{itemize}

\section{{\bfseries\sffamily TODO} \cite{rashid2016atmospheric}}
\label{sec:org826e0bc}
\section{{\bfseries\sffamily TODO} \cite{ropelewski1987global}}
\label{sec:orgc7c5d50}
\section{{\bfseries\sffamily TODO} \cite{son2010impact}}
\label{sec:org8390afa}
\section{{\bfseries\sffamily TODO} \cite{stevenson2010enso}}
\label{sec:org7d57c16}
\section{{\bfseries\sffamily TODO} \cite{stevenson2012will}}
\label{sec:orge0c0888}

\section{\cite{stevenson2012significant}}
\label{sec:orgc796e1b}

\begin{itemize}
\item CMIP5 dataset
\item No significant change in ENSO amplitude for multi-model mean during 20-21st century
\item Some significant changes in certain models
\item Larger ensembles are needed
\end{itemize}

\section{\cite{stevenson2017forced}}
\label{sec:orgcf41ef7}

\begin{itemize}
\item ENSO diversity: difference between CP and EP ENSO events
\item CESM Last Millennium ensemble
\item Less forced impact on ENSO amplitude, some impact on diversity
\item Lots of natural factors have an impact too
\end{itemize}

\section{\cite{torrence1998practical}}
\label{sec:org1dc9592}

@@

\section{{\bfseries\sffamily TODO} \cite{vecchi2006weakening}}
\label{sec:orgbbf1261}

\section{\cite{vega2017analysis}}
\label{sec:org27d5f82}

\begin{itemize}
\item Control and global warming forced simulations
\item Lots of internal variability
\end{itemize}

\section{{\bfseries\sffamily TODO} \cite{wang2016nino}}
\label{sec:org937c167}
\section{{\bfseries\sffamily TODO} \cite{yeo2016role}}
\label{sec:orgf9d0601}
\section{{\bfseries\sffamily TODO} \cite{zhang2019review}}
\label{sec:orgfbc580a}
\section{{\bfseries\sffamily TODO} \cite{zheng2016intermodel}}
\label{sec:orgbd6185d}

\section{\cite{zheng2017response}}
\label{sec:orgcd8dd72}

\begin{itemize}
\item CESM-LE ensemble
\item Lots of internal variability
\item At least 15 models are necessary to separate forced from internal variability
\end{itemize}

\bibliographystyle{apalike}
\bibliography{../references}
\end{document}
